---
title: "chromaticity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{chromaticity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "#>"
)
```

```{r setup}
library(chromaticity)
library(ggplot2)

gphtheme <- theme(axis.title.y = element_text(margin = margin(r = 10)),
                  axis.title.x = element_text(margin = margin(t = 10)),
                  axis.line = element_line(size = 0.5),
                  axis.ticks = element_blank(),
                  legend.title = element_blank(),
                  legend.text = element_text(hjust=0.1),
                  legend.key = element_blank(),
                  legend.position = "bottom",
                  legend.spacing = unit(1.0,"cm"),
                  legend.key.size = unit(1.5,"lines"),
                  plot.margin=grid::unit(c(10,10,5,5), "mm"),
                  panel.grid.major.y = element_line(size = 0.25,color="grey70"),
                  panel.grid.minor.y = element_line(size = 0.25,color="grey70"),
                  panel.grid.major.x = element_blank(),
                  panel.grid.minor.x = element_blank(),
                  panel.background = element_blank(),
                  strip.background = element_blank()) 
```

The purpose of this package is to ensure that color palettes are optimized for the number of colors selected by the user. For each of the four palettes provided by `color_pickr`, a different subset of the colors is returned based on the number of colors selected by the user. Examples of the color palettes are provided in the following sections.

### Jalama

```{r}
for (xx in 1:10) {

    test <- data.frame(variable = factor(1:xx, levels = 1:xx), value = 1)

    print(
      ggplot(test, aes(variable, value, fill = variable)) +
        geom_bar(stat = "identity") +
        scale_fill_manual(values = color_pickr(xx, "Jalama")) +
        gphtheme +
        theme(legend.position = "none") +
        labs(x = NULL, y = NULL)
      
    )

}
```



### Refugio

```{r}
for (xx in 1:7) {

    test <- data.frame(variable = factor(1:xx, levels = 1:xx), value = 1)

    print(
      ggplot(test, aes(variable, value, fill = variable)) +
        geom_bar(stat = "identity") +
        scale_fill_manual(values = color_pickr(xx, "Refugio")) +
        gphtheme +
        theme(legend.position = "none") +
        labs(x = NULL, y = NULL)
      
    )

}
```

### Rincon

```{r}
for (xx in 1:7) {

    test <- data.frame(variable = factor(1:xx, levels = 1:xx), value = 1)

    print(
      ggplot(test, aes(variable, value, fill = variable)) +
        geom_bar(stat = "identity") +
        scale_fill_manual(values = color_pickr(xx, "Rincon")) +
        gphtheme +
        theme(legend.position = "none") +
        labs(x = NULL, y = NULL)
      
    )

}
```

### El Capitan

```{r}
for (xx in 1:9) {

    test <- data.frame(variable = factor(1:xx, levels = 1:xx), value = 1)

    print(
      ggplot(test, aes(variable, value, fill = variable)) +
        geom_bar(stat = "identity") +
        scale_fill_manual(values = color_pickr(xx, "El Capitan")) +
        gphtheme +
        theme(legend.position = "none") +
        labs(x = NULL, y = NULL)
      
    )

}
```


